### 2020-03-05 defesa/tex/chapter/mcd2.tex
wip

For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
Ellipses are also strictly convex bodies, given an axis-parallel ellipse with shape parameters $(a, b)$, a norm $||\cdot||_{a,b}$ can be defined, such that its unit disk is the coverage region of that ellipse.

From now on, since ellipses are just unit circles in a strictly convex normed space $(\R^2, ||\cdot||_{a,b})$, with $||\cdot||_{a, b}$ being an elliptical norm whose unit disk is an ellipse with shape parameters $(a, b)$, we will develop this work for any set of strictly convex unit disks.

>>>>

For example, the norms $||\cdot||_p$, $p\in \mathbb{N}, p>1$ define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a norm $||\cdot||_{a,b}$, such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.

%In the next section we introduce a problem equivalent to MCE with only one facility.

%This way, from now on we will consider a more general version of MCE whose instance is composed by a set of strictly convex norms $\F:=\{f_1, \dots, f_m\}$, instead of the list of shape parameters $\Rr$, and the list $\E:=\{E_1, \dots, E_m\}$ having $ .
